Unifying Lower Bounds on Prediction Dimension of Consistent Convex Surrogates

### 2021-01-28 colt-21/cvx-flats.tex
Adding BEP to example in S5

\paragraph{Example: New bounds for high-confidence classification.}\label{subsec:examples-finite}
When given a target loss, we can consider the \emph{abstain property} of~\citet{ramaswamy2018consistent} over 3 outcomes where one wishes to predict the most likely outcome $y$ if $Pr[Y=y|x] \geq 1/2$ and ``abstain'' by predicting $\bot$ otherwise.
This is elicited by the target loss $\ell^{abs}(r,y) := \Ind{r \not \in \{y, \bot\}} + (1/2)\Ind{r = \bot}$. 
To lower bound the dimension of convex surrogates, we can consider two different distributions; in the first, our bound yields a strict gap over the feasible subspace dimension bound, and in the second, the bounds are equal.
First, we choose $p$ to be the uniform distribution (black dot in Figures~\ref{fig:fsd-bound} and~\ref{fig:flats-bound}).
In this case, the bound by feasible subspace dimension yields $\conscvx(\ell^{abs}) \geq 3 - 2 - 1 = 0$, as the feasible subspace dimension is $2$ since we are on the relative interior of the level set and simplex, as shown in Figure~\ref{fig:fsd-bound}.
\jessie{Talk about BEP? though less detail than old intro- mention tight bounds for $n = 3$.}

@@

However, consider any $1$-flat containing $p$ (the uniform distribution).
When intersected with the simplex, one can see that any line in the simplex through $p$ also leaves the cell $\gamma_\bot$, which contains $p$.
See Figure~\ref{fig:flats-bound} for intuition; a $1$-flat through $p \in \relint{\simplex}$ would be a line in such a figure.
Therefore, we have no $1$-flat containing $p$ staying in $\gamma_\bot$, so we obtain a better lower bound, $\conscvx(\ell^{abs}) \geq 2$.

>>>>

\paragraph{Example: New bounds for high-confidence classification.}\label{subsec:examples-finite}
When given a target loss, we can consider the \emph{abstain property} over 3 outcomes where one wishes to predict the most likely outcome $y$ if $Pr[Y=y|x] \geq 1/2$ and ``abstain'' by predicting $\bot$ otherwise.
This is elicited by the target loss $\ell^{abs}(r,y) := \Ind{r \not \in \{y, \bot\}} + (1/2)\Ind{r = \bot}$. 
\citet{ramaswamy2016convex} present a convex surrogate for the abstain target loss that takes as input a prediction whose dimension is logarithmic in the number of outcomes, yielding new upper bounds on $\conscvx(\ell^{abs})$ which are an exponential improvement over previous results, e.g.,~\cite{crammer2001algorithmic}.
To lower bound the dimension of convex surrogates, we can consider two different distributions; in the first, our bound yields a strict gap over the feasible subspace dimension bound, and in the second, the bounds are equal.
First, we choose $p$ to be the uniform distribution (black dot in Figures~\ref{fig:fsd-bound} and~\ref{fig:flats-bound}).
In this case, the bound by feasible subspace dimension yields $\conscvx(\ell^{abs}) \geq 3 - 2 - 1 = 0$, as the feasible subspace dimension is $2$ since we are on the relative interior of the level set and simplex, as shown in Figure~\ref{fig:fsd-bound}.

@@

However, consider any $1$-flat containing $p$ (the uniform distribution).
When intersected with the simplex, one can see that any line in the simplex through $p$ also leaves the cell $\gamma_\bot$, which contains $p$.
See Figure~\ref{fig:flats-bound} for intuition; a $1$-flat through $p \in \relint{\simplex}$ would be a line in such a figure.
Therefore, we have no $1$-flat containing $p$ staying in $\gamma_\bot$, so we obtain a better lower bound, $\conscvx(\ell^{abs}) \geq 2$.
Combining this with the upper bounds given by~\cite{ramaswamy2018consistent}, we observe the bound $\conscvx(\ell^{abs}) = 2$ is tight.
